% chktex-file 8

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}

% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% CV Info (to be customized).
\newcommand{\CVAuthor}{Mahdi Mir}

% % PDF settings and properties.
% \hypersetup{
% pdfauthor={\CVAuthor},
% pdfcreator={XeLaTeX},
% pdfproducer={},
% pdfkeywords={},
% unicode=true,
% bookmarks=true,
% bookmarksopen=true,
% pdfstartview=FitH,
% pdfpagelayout=OneColumn,
% pdfpagemode=UseOutlines,
% hidelinks,
% breaklinks
% }

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% VARIABLES.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\teias}{\href{https://teias.institute}{TeIAS}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%


\Title{\CVAuthor}

\begin{SubTitle}

    \par
    \href{mailto:imahdimir@gmail.com}{imahdimir@gmail.com}
    \ \SubBulletSymbol\
    +98\ (902)\ 35-35-912
    \ \SubBulletSymbol\
    \href{https://github.com/imahdimir}{GitHub.com/imahdimir}

\end{SubTitle}


\begin{Body}

    %%%%%%%%%%%%%%%
    %% EDUCATION %%
    %%%%%%%%%%%%%%%

    \Section{Education}{Education}{PDF:Education}

    \Entry{\textbf{Master's in Theoretical Economics}, \textit{\teias, Tehran, Iran}}
    \hfill
    {2019} -- {2022}

    \Gap{}

    \BulletItem{Full-tuition \textbf{scholarship} with a stipend for graduate studies. \\ \textbf{One of 16} awardees \textbf{nationwide.}}
    \BulletItem{{Thesis: ``Do Iranian mutual funds follow momentum or anti-momentum strategies?''\\Supervised by Mahdi Heidari.}}
    \BulletItem{GPA:\ 4}

    \BigGap{}

    \Entry{\textbf{B.Sc.\ in Electrical Engineering}}, \textit{Sharif University of Technology, Tehran.}
    \hfill
    {2013} -- {2019}


    \Gap{}

    \BulletItem{\textbf{Ranked \boldmath{\(162^{nd}\)}} in nationwide university entrance examination for Bachelor programs \newline among more than \boldmath{\(250K\)} participants.}
    \BulletItem{Thesis:\ ``How to design an efficient solar energy production system?''\\
        Supervised by Ali Abbaspour (\textbf{MIT} \& \textbf{Berkeley} Alumni).}


    %%%%%%%%%%%%%%%%%%%%%%%%%
    %% Computer Skills %%
    %%%%%%%%%%%%%%%%%%%%%%%%%

    \Section{Computer skills}{Computer Skills}{PDF:Computer Skills}

    \Entry{\textbf{Programming Languages}}

    \Gap{}
    \Gap{}

    \BulletItem{\textbf{STATA}, \textit{Professional level}}
    \begin{Detail}
        \SubBulletItem{Estimation of different econometrics models, like fixed Effect, Logit \& probit, ordinary OLS \& etc.}
        \SubBulletItem{High-Dimensional fixed effect models, with thousands of categories using \textbf{REGHDF} package.}
        \SubBulletItem{Various data visualization practices.}
        \SubBulletItem{Implementiation of time series regression models.}
        \SubBulletItem{Worked with Large Scale Datasets. e.g. HAN 2022, REGPAT 2022 and Orbis.}
    \end{Detail}

    \Gap{}
    \Gap{}

    \BulletItem{\textbf{Python}, \textit{Professional level}}

    \Gap{}

    \begin{Detail}
        \SubBulletItem{Expreience in \textbf{layout parsing} of the financial statements images using \href{https://arxiv.org/abs/2001.01469}{the \textbf{\textit{TableNet} deep learning model.}}}
        \SubBulletItem{Good experience in \textbf{image processing} and \textbf{OCR}, using the Google Tesseract engine, for Persian language.}
        \SubBulletItem{Deep experience in textual analysis, working with texts \& regular expressions.}
        \SubBulletItem{Quantitative analysis in finance.}
        \SubBulletItem{Data mining and data crawling from the internet HTML pages.}
        \SubBulletItem{Various data cleaning/gathering projects using Pandas, etc.}
        \SubBulletItem{Various interactive \textbf{data visualization} and statistical analysis.}
        \SubBulletItem{Designed a pattern match checking system for tables (2-D data).}
        \SubBulletItem{Deep experience in \textbf{multiprocessing} \& \textbf{asynchronous} processing to speed-up projects.}
    \end{Detail}

    \Gap{}
    \Gap{}

    \BulletItem{\textbf{R}, \textit{Uppper-Intermediate level}}

    \Gap{}

    \begin{Detail}
        \SubBulletItem{Calculation of \textbf{PDF} and \textbf{CDF} functions numerically.}
        \SubBulletItem{Multivarite \textbf{regression} and \textbf{time series} analysis.}
        \SubBulletItem{Implementation of \textbf{Monte Carlo} simulations.}
        \SubBulletItem{Implementation of \textbf{Markov Chain Monte Carlo} algorithms.}
        \SubBulletItem{Estimation of \textbf{non-linear} regression models.}
    \end{Detail}

    \BulletItem{\textbf{Julia}, \textit{Intermediate level}}
    \Gap{}
    \begin{Detail}
        \SubBulletItem{Dynamic programming, finding value functions quantitatively.}
        \SubBulletItem{Quantitative analysis in the labor field.}
        \SubBulletItem{Implementing McCall job search model and its succeeding models.}
        \SubBulletItem{Various data visualization practices.}
        \SubBulletItem{Done several comparative statistical analyses in the context of labor search models.}
    \end{Detail}

    \Gap{}
    \Gap{}

    \BulletItem{\textbf{Visual Basic}, \textit{Intermediate level}}
    \Gap{}
    \begin{Detail}
        \SubBulletItem{Mostly coding in Excel.}
    \end{Detail}

    \Gap{}
    \Gap{}

    \BulletItem{\textbf{C, C++}, \textit{Basic level}}
    \begin{Detail}
        \SubBulletItem{Done some basic projects.}
    \end{Detail}

    \BulletItem{\textbf{Bash}, \textit{Intermediate level}}
    \begin{Detail}
        \SubBulletItem{Database upgrade automation in Linux environment.}
    \end{Detail}

    \BigGap{}

    \Entry{\textbf{Others}}

    \Gap{}
    \Gap{}



    \BulletItem{\textbf{MySQL}, \textit{Intermediate level}}
    \begin{Detail}
        \SubBulletItem{Worked with standard and global databases like \href{https://www.bvdinfo.com/en-gb/solutions-for-your-role/corporate-finance-and-ma-research}{\textbf{Zepyhr}}, \href{https://www.bvdinfo.com/en-gb/our-products/data/international/orbis}{\textbf{Orbis}}, \href{https://www.oecd.org/sti/inno/intellectual-property-statistics-and-analysis.htm}{\textbf{OECD PATENTS}},\\
            the \href{https://icrios.unibocconi.eu/resources/databases/patents-icrios-database}{\textit{\textbf{Bocconi}} university \textbf{PATENTS-ICRIOS} database}, etc.}
    \end{Detail}

    \BulletItem{\textbf{MATLAB, Octave}, \textit{Preofessional level}}
    \begin{Detail}
        \SubBulletItem{Mostly working with matrices, quantitative simulation \& analyses}
    \end{Detail}
    \BulletItem{\textbf{Dynare}, \textit{Intermediate level}}
    \begin{Detail}
        \SubBulletItem{Simulation of DSGE models.}
    \end{Detail}

    \BulletItem{\textbf{\LaTeX, Beamer}, \textit{Professional level}}
    \BulletItem{\textbf{MS Excel, Word, PowerPoint}, \textit{Professional level}}
    \BulletItem{\textbf{Linux (Ubuntu)}, \textit{Upper-Intermediate level}}
    \BulletItem{\textbf{Windows}, \textit{Advanced level}}
    \BulletItem{\textbf{Mac OS}, \textit{Advanced level}}

    %%%%%%%%%%%%%%%%%%%%%%%%%
    %% RESEARCH EXPERIENCE %%
    %%%%%%%%%%%%%%%%%%%%%%%%%

    \Section{Research Experiences \newline \& \newline Computer Projects}{Research Experience}{PDF:Research Experience}

    \Entry{\textbf{Graduate Economics Student}, \textit{\teias}}
    \hfill
    {2019} -- {2022}

    \Gap{}
    \Gap{}

    \BulletItem{Data extraction from the mutual funds' reports' images about their holdings, using image processing methods, \textbf{Google Tesseract} engine and  \href{https://arxiv.org/abs/2001.01469}{the \textbf{\textit{TableNet} deep learning model.}} As a part of my Master's thesis data gathering.}
    \BulletItem{Data crawling of the Iranian firms' monthly revenue from HTML \& also scanned images.}
    \BulletItem{Replication of the paper \href{https://doi.org/10.1111/j.1540-6261.1993.tb04702.x}{Jegadeesh, Titman (1993), ``Returns to Buying Winners and Selling Losers: Implications for Stock Market Efficiency''}, with Iran's stocks market data. Supervised by Mahdi Heidari.}
    \BulletItem{Done several back-testing of trading strategies using the \href{https://zipline.ml4trading.io/}{\textbf{Zipline}} open source backtesting library, and \href{https://github.com/quantopian/alphalens}{\textbf{AlphaLens engine.}} in Python.}
    \BulletItem{Done some adjustments in the source code of \href{https://zipline.ml4trading.io/}{\textbf{Zipline}} for backtesting of momentum strategies with Iran's market historical data.}
    \BulletItem{Replication of the paper \href{https://doi.org/10.1016/j.jbankfin.2006.10.029}{Ng, Wu (2007), ``The trading behavior of institutions and individuals in Chinese equity markets''}, with Iran's stocks market data. Supervised by Mahdi Heidari.}
    \BulletItem{Implementing McCall search \& other related models with Julia. Supervised by Hossein Joshaghani.}
    \BulletItem{Worked with Macroeconomics databases, gathered \& cleaned Iran's
        risk-free rate, exchange rates, gold prices and some more.}

    \BigGap{}

    \Entry{\textbf{Others}}

    \Gap{}

    \BulletItem{Authority \& Innovation, \href{https://www.bwl.uni-mannheim.de/en/maug/team/hamed-davari/}{\textbf{\textit{Hamed Davari, University of Mannheim, Germany.}}}}
    \hfill
    \DatestampYM{2022}{07}

    \begin{Detail}
        \SubBulletItem{Worked with \href{https://www.bvdinfo.com/en-gb/solutions-for-your-role/corporate-finance-and-ma-research}{\textbf{Zepyhr} Database}, the Comprehensive M\&A data with integrated detailed company information, from Bureau van Dijk, A Moody's Analytics Company}
        \SubBulletItem{Worked with \href{https://www.bvdinfo.com/en-gb/our-products/data/international/orbis}{\textbf{Orbis} database}, a growing database of companies and other entities, from Bureau van Dijk, A Moody's Analytics Company}
        \SubBulletItem{Worked with \href{https://www.oecd.org/sti/inno/intellectual-property-statistics-and-analysis.htm}{OECD Patent datasets}}
        \SubBulletItem{Worked with \href{https://icrios.unibocconi.eu/resources/databases/patents-icrios-database}{PATENTS-ICRIOS DATABASE}, from the Bocconi university, Italy}
    \end{Detail}

    \BulletItem{Iran's listed firms' employment details, \href{https://www.javadshamsi.com/}{\textbf{\textit{Javad Shamsi, LSE, UK.}}}}
    \hfill
    \DatestampYM{2022}{09}

    \begin{Detail}
        \SubBulletItem{Gathered a dataset of industry and subindustry of listed firms, and their matching with standard \textbf{ISIC} codes version 4.}
        \SubBulletItem{Worked on adjusted/not adjusted prices of listed firms.}
    \end{Detail}


    \Section{\texorpdfstring{Research Assistant}{}}
    {\texorpdfstring{Research Assistant}{}}
    {PDF:Research Assistant}

    \BulletItem{Mahdi Heidari, \textbf{\textit{\teias, 30 months}}}
    \hfill
    {2020} -- {2022}

    \BulletItem{\href{https://www.bwl.uni-mannheim.de/en/maug/team/hamed-davari/}{Hamed Davari, \textbf{\textit{University of Mannheim, Germany, 4 months}}}}
    \hfill
    {Summer 2022}

    \BulletItem{\href{https://www.javadshamsi.com/}{Javad Shamsi}, \textbf{\textit{Starting Sep 2022, Ongoing}}}
    \hfill
    {2022}



    \Section{\texorpdfstring{Teaching Assistant}{}}
    {\texorpdfstring{Teaching Assistant}{}}
    {PDF:Teaching Assistant}

    \Entry{\textbf{TeIAS}}

    \BulletItem{Fintech, \href{https://aminshams.com/}{\textbf{\textit{Amin Shams, Fisher College of Business, OSU, USA.}}}}
    \hfill
    {2022}

    \BulletItem{Macroeconomics I, \textit{Hosein Joshagahni}}
    \hfill
    {2021}

    \BulletItem{Microeconomics I, \textit{Sepehr Ekbatani}}
    \hfill
    {2020}

    \Entry{\textbf{Sharif University of Technology}}
    \BulletItem{Electrical Engineering Principles}
    \hfill
    {2017}

    \Section{\texorpdfstring{Other Professional Activities}{}}
    {\texorpdfstring{Other Professional Activities}{}}
    {PDF:Other Professional Activities}


    \BulletItem{Head Manager of Economic/Financial Databases, \textit{\teias}}
    \hfill
    {2021} -- {2022}

    \BulletItem{Corporate Governance Reading Group, \textit{\teias}}
    \hfill
    {2021}

    \BigGap{}


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% AWARDS, Honors & SCHOLARSHIPS %%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \Section{\texorpdfstring{Awards,\newline Honors \&\newline Scholarships}{}}
    {\texorpdfstring{Awards -\newline Honors \&\newline Scholarships}{}}
    {PDF:Awards, Honors, and Scholarships}


    \BulletItem{\textbf{Full-tuition \textit{scholarship}} with a stipend for graduate studies,    \hfill
        {2019} \\ for the \textbf{Master's of Theoretical Economics}, \teias, \textbf{One of 16} awardees \textbf{nationwide.}}

    \Gap{}


    \BulletItem{\textbf{Ranked \boldmath{\(79^{th}\)}} in the nationwide university entrance examination for the Master's in Economics.}
    \hfill
    \DatestampY{2019}

    \Gap{}

    \BulletItem{\textbf{Ranked \boldmath{\(162^{nd}\)}} in nationwide university entrance examination for Bachelor programs \hfill {2013} \newline among more than \boldmath{\(250K\)} participants.}

    \Gap{}

    \BulletItem{Accpeted in the first stage of national \textbf{Mathematics olympiad}}
    \hfill
    \DatestampY{2012}


    \Section{\texorpdfstring{Litretaure Review}{}}
    {\texorpdfstring{Litretaure Review}{}}
    {PDF:Litretaure Review}

    \BulletItem{\href{https://github.com/imahdimir/corporate-governance-litretaure-review-summer-2020/blob/main/L.R.%20Report%20V.2.pdf}{Corporate Governance: A Brief Review of the Litretaure}}
    \hfill
    \DatestampY{2020}

    \BigGap{}

    \Section{\texorpdfstring{Working \newline Papers}{}}
    {\texorpdfstring{Working Papers}{}}
    {PDF:Working Papers}


    \BulletItem{``Do Iranian mutual funds follow momentum or anti-momentum strategies?'' with Mahdi Heidari.}
    \BulletItem{``Good News, Bad News About Iranian Listed Firms, the First Dataset in Iran.'' with Mahdi Heidari.}


    %%%%%%%%%%%%%%%
    %% LANGUAGES %%
    %%%%%%%%%%%%%%%

    \Section{Languages}{Languages}{PDF:Languages}

    \Entry{\textbf{English}, Upper-intermediate level}
    \Entry{\textbf{Persian}, Native, Fluent}


    %%%%%%%%%%%%%%%%%%%%%%%
    %% Relevant Courses %%
    %%%%%%%%%%%%%%%%%%%%%%%

    \Section{Relevant Graduate courses}{Relevant Graduate courses}{PDF:Relevant Graduate courses}


    \Entry{\textbf{Macroeconomics II}}, \textit{Hosein Joshaghani, \teias}
    \hfill
    {Fall 2021}

    \BulletItem{Contents: Fiscal Multiplier \& Identification in Macro, Dynamic Optimization,\\Bellamn Equation, Continuous-Time Search Models, Discrete-Time search models, Consumption, Investment, Financial Markets.}
    \BulletItem{Grade: \(A\)}

    \Entry{\textbf{Topics in Macro, Labor Market \& Search}}, \textit{Alireza Sepah-Salari (\textbf{University of Bristol})}
    \hfill
    {Spring 2021}

    \BulletItem{Dynamic Programming, Bellman Equation, general equilibrium models with\\incomplete financial
        markets, Huggett (1993), Aiyagari (1994), heterogeneous agents models.}


    \Entry{\textbf{Financial Economics II}}, \textit{Farshad HaghPanah, \teias}
    \hfill
    {Fall 2020}

    \BulletItem{Investment Management \& Corporate Finance, Asset Pricing, Market Microstructure}
    \BulletItem{Grade: \(A^{-}\)}

    \Entry{\textbf{Microeconomics II, Game Theory}}, \textit{Mahdi Fadaei, \teias}
    \hfill
    {Fall 2020}
    \BulletItem{Strategic-Form Games, Mixed Strategies, Continuous Games, Bayesian Games, Extensive-Form Games, Perfect-Bayesian Equilibrium, Repeated Games.}
    \BulletItem{Grade: \(A\)}

    \Entry{\textbf{Macroeconomics I}}, \textit{Hosein Joshaghani, \teias}
    \hfill
    {Spring 2020}
    \BulletItem{Solow growth model, Neo-Classical Growth Model, Endogenous Growth Model, Real Bussiness Cycle Theory, Nominal Rigidity, DSGE Models}
    \BulletItem{Grade: \(A^{-}\)}

    \Entry{\textbf{Econometrics II}}, \textit{Muhamad Hoseini, \teias}
    \hfill
    {Spring 2020}
    \BulletItem{Causality, Regression, Maximum Likelihood Estimation, GMM, Binary Response Models, Selection Bias \& Experiments, IV, DID, Regression Discountinuity.}
    \BulletItem{Grade: \(A\)}

    \Entry{\textbf{Financial Economics I}}, \textit{Mahdi Heidari, \teias}
    \hfill
    {Fall 2019}
    \BulletItem{Time Value of Money, Corporate Valuation Models, Modern Portfolio Theory, Capital Asset Pricing Model (CAPM), Efficient Market Hypothesis, Introduction to Derivatives.}
    \BulletItem{Grade: \(A\)}

    \Entry{\textbf{Econometrics I}}, \textit{Layla Shiva, \teias}
    \hfill
    {Fall 2019}
    \BulletItem{Simple Regression, Multiple Regression, Inferences, Dummy Variable, IV, Two Stage Leaset Squares, Simultaneous Equations Models.}
    \BulletItem{Grade: \(A\)}

    \Entry{\textbf{Mathematics For Economics}}, \textit{Erfan Salavati, \teias}
    \hfill
    {Fall 2019}
    \BulletItem{Matrices, Linear Algebra, Concave \& Convex Functions, Constraind \& Un-Constrained Optimization, Kuhn-Tucker Theorem.}
    \BulletItem{Grade: \(A^{-}\)}

    \Entry{\textbf{Microeconomics I}}, \textit{Muhamad Morovati, \teias}
    \hfill
    {Fall 2019}
    \BulletItem{Choice Theory, Classical Demand Theory, Aggreagate Demand, Production, Uncertaintity, General Equilibrium Theory.}
    \BulletItem{Grade: \(A^{-}\)}

    \Entry{\textbf{Macroeconomics}}, \textit{Morteza Zamanian, GSME at Sharif University of Technology}
    \hfill
    {Spring 2019}
    \BulletItem{Bonds Market, The IS-LM Model, The AS-AD Model, The Phillips Curve.}
    \BulletItem{Grade: \(A\)}


    %%%%%%%%%%%%%%%%%%%%%%
    %% Summer Schools %%
    %%%%%%%%%%%%%%%%%%%%%%


    \Section{Summer \newline Schools \&\newline Short-term Studies}
    {Summer Schools}
    {PDF:Summer Schools}

    \BulletItem{\textbf{\boldmath{\(2^{nd}\)} International Trade}, \textit{Summer School, \teias}}
    \hfill
    \DatestampY{2019}

    \BulletItem{\textbf{Data Science}, \textit{Winter School, \teias}}
    \hfill
    \DatestampY{2020}

    \BulletItem{\textbf{Theoretical Aspects of Data Science and Machine Learning}, \textit{Summer School, \teias}}
    \hfill
    \DatestampY{2022}


    \BigGap{}


    \Section{\texorpdfstring{Hobbies}{}}
    {\texorpdfstring{Hobbies}{}}
    {PDF:Hobbies}

    \BulletItem{Swimming, Professional Level, life-saving Certificate, from ISAF, Iran Ministry of Sports \& Youth.}


\end{Body}


\end{document}